\huge Tor's Usability for Censorship Circumvention

### 2016-10-14 pets2017-paper/pets2017-paper.tex
editing pass through introduction.

  \begin{abstract}
{
We evaluate, design, and test the Tor configuration interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interface interactions.
A 16-participant qualitative study examines user assumptions and common mistakes.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative study shows that our design changes result in
a significant reduction in time. We conclude with recommendations for changes 
to the current interface as well as alternative solutions.}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Tor is an anonymity network that routes traffic through a series of relays
that make it difficult to observe the source and destination~\cite{dingledine2004tor}. Tor's anonymizing functionality also circumvents censorship. Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.

This is the first user study that investigates the usability of Tor as a censorship circumvention tool. Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier. All Tor users benefit from improving the configuration interface, and thereby increasing the adoption of Tor as a censorship circumvention tool. Users who successfully use Tor to circumvent censorship are provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.

We evaluate, redesign, and test Tor's configuration interface by
measuring participants' interactions with the interface in various censorship environments.
The first user study is a small-scale, qualitative experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, quantitative experiment
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

In this paper, we contribute the following:
\smallskip
\begin{itemize}
\item 6 common challenges encountered during the configuration process and their underlying causes
\item 10 changes to the configuration interface which we hope alleviates the common challenges
\item 114 logs of real world user attempts to connect to Tor in three different censorship environments
\item 4 reasons why users failed to connect to Tor
\item 5 recommendations of configuration interface changes to help more users connect and save time
\item 5 alternative  approaches to bootstrapping a connection that leverage varying degrees of automation
\end{itemize}
We hope that our work helps users circumvent censorship and connect to Tor.

\section{Related Work} 
There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests, and prevents user adoption. 
Norcie et~al.~\cite{norcie2012eliminating} found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

@@

\section{Background}
This section provides the necessary background the configuration interface relates to Tor, the network components that are involved in censorship circumvention, and the configuration settings are required to bypass levels of Tor-adverse censorship environments.

\subsection{Tor, Tor Browser, and Tor Launcher}
The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
a modified Firefox browser that includes a built-in Tor client.
Tor Browser has a component called Tor Launcher that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface gives access to 
sophisticated circumvention mechanisms, giving the user
the option to configure a proxy and bridge before connecting to Tor
for the first time. This is the object of our study.

In principle, the process of configuring a proxy and bridge can be automated, but
the interface eschews automatic configuration through network probing
in favor of guided manual configuration to give users agency in configuring their connection. 
Automatic configuration through network probing may put some users in certain regimes at risk. 
A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
However, this requires that the user grapple with technical concepts such as 
bridges, pluggable transports, and proxies. Some of these concepts are specific to 
Tor and not general concepts.

@@

\subsection{Circumventing Censorship with Tor}
There are many valid configuration settings to connect to the Tor network.
For instance, a user who does not need a bridge or proxy 
can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
The minimum amount of configuration required, therefore, the set of valid configuration settings,
vary depending on the censorship environment. In the worst case, users must know or find out:\\

@@

\section{Evaluation Criteria and Goals}
\label{sec:goals}
Our user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled OLD in our figures and tables,
is the current version being distributed with Tor Browser.
The second, NEW, is the prototype that we designed
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

@@

\section{Future Work} 
Our goal was to deploy impactful, tested changes the Tor configuration interface. In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface. Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away. For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed. However, we list some alternative approaches that seem worth exploring. \\

>>>>

  \begin{abstract}
{
We evaluate, design, and test the Tor Launcher interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interface interactions.
A 16-participant qualitative study examines user assumptions and common mistakes.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative study shows that our design changes result in
a significant reduction in time. We conclude with recommendations for changes 
to the current interface as well as alternative solutions.}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
that make it difficult to observe the source and destination. 
Tor Browser~\cite{torbrowser}, a modified Firefox browser with a built-in Tor client, 
is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface asks the user to configure
bridges, pluggable transports, and proxies to make a connection to Tor (we refer to as the ``configuration interface'' throughout this paper). This is the object of our study.

We start by introducing terms (section~\ref{sec:background}) and, 
describing the experimental setup (section~\ref{sec:environments}). 
Then we report of user observations and interviews (section~\ref{sec:qualitative}),
evaluate the current interface (section~\ref{sec:eval}), 
list design principles and interface changes (section~\ref{redesign}),
measure the impact of changes in the quantitative experiment in section~\ref{sec:quantitative}, 
testing measured the impact of the design changes (Section~\ref{sec:quantitative}, and
discuss user behaviors (section~\ref{sec:discussion}).
We end with limitations (section~\ref{sec:limitations}), 
related work (section~\ref{sec:related}), 
future work (section~\ref{sec:future}), and
a conclusion (section~\ref{sec:conclusion}).

We contribute:
\smallskip
\begin{itemize}
\item an evaluation of the current configuration interface
\item a redesigned configuration interface
\item logs of 114 users' connection attempts
\item failure modes seen during connection attempts
\item recommended interface changes
\item alternative bootstrapping approaches
\end{itemize}
We hope that our work helps users circumvent censorship and connect to Tor.

\section{Related Work}
\label{sec:related} 
There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests, and prevents user adoption. 
Norcie et~al.~\cite{norcie2012eliminating} found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

@@

\section{Background}
\label{sec:background}
This section provides the necessary background the configuration interface relates to Tor, the network components that are involved in censorship circumvention, and the configuration settings are required to bypass levels of Tor-adverse censorship environments.

@@

\subsection{Connecting to Tor}
There are many valid configuration settings to connect to the Tor network.
For instance, a user who does not need a bridge or proxy 
can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
The minimum amount of configuration required, therefore, the set of valid configuration settings,
vary depending on the censorship environment. In the worst case, users must know or find out:\\

@@

\subsection{Potential for good} 
%Tor's anonymizing functionality also circumvents censorship. Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.

%This is the first user study that investigates the usability of Tor as a censorship circumvention tool. Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier. All Tor users benefit from improving the configuration interface, and thereby increasing the adoption of Tor as a censorship circumvention tool. Users who successfully use Tor to circumvent censorship are provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.

\section{Evaluation Criteria}
\label{sec:eval}
Our user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled OLD in our figures and tables,
is the current version being distributed with Tor Browser.
The second, NEW, is the prototype that we designed
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

@@

\section{Future Work} 
%In principle, the process of configuring a proxy and bridge can be automated, but
%the interface eschews automatic configuration through network probing
%in favor of guided manual configuration to give users agency in configuring their connection. 
%Automatic configuration through network probing may put some users in certain regimes at risk. 
%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
%However, this requires that the user grapple with technical concepts such as 
%bridges, pluggable transports, and proxies. Some of these concepts are specific to 
%Tor and not general concepts.

Our goal was to deploy impactful, tested changes the Tor configuration interface. In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface. Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away. For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed. However, we list some alternative approaches that seem worth exploring. \\
